A general approach to maximise information density in neutron reflectometry analysis

### 2020-03-05 paper/paper.tex
add zenodo

Electronic Supplementary Information (ESI) available: All analysis/plotting scripts and data files allowing for a fully reproducible, and automated, analysis workflow for the work presented is available at \url{https://github.com/arm61/model\_select} (DOI: 10.5281/zenodo.xxxxxxx) under a CC BY-SA 4.0 license.

>>>>

Electronic Supplementary Information (ESI) available: All analysis/plotting scripts and data files allowing for a fully reproducible, and automated, analysis workflow for the work presented is available at \url{https://github.com/arm61/model\_select} (DOI: 10.5281/zenodo.3697795) under a CC BY-SA 4.0 license.
